Graph bipartitioning and you

### 2016-01-29 evolutionaryComputation/2-practical/report.tex
can do stastical significant stuff now, although I don't claim to understand it.
now can generate tables properly also started working on fidducia and mathesis search

Doing this 30 times to cancel the staostic effect would result into ~5 hours.
\section{TODO}
MLS with several results
GLS -> I think the localsearch will recursively unecesrly decend into its members
because the local search is packed in the member factory. Maybe remove the
local search from the memberfactory?

\pgfplotstableread{dataTable.txt}\dataTable
\begin{tikzpicture}
\pgfplotsset{set layers}
\begin{axis}[
	ybar stacked,
	xlabel={Algorithm},
	xticklabels from table={dataTable.txt}{name},
	xtick=data,
	ylabel={Time}
]

@@

\end{empfile}
\end{document}

>>>>

Doing this 30 times to cancel the staostic effect would result into ~5 hours.

\subsection{Counting double}
I had an issue in which my classmates would get much better results than me.
After discussing it for a while it turned out that I was counting double. However
This didn't make sense because I just used scala combinators to count the 
elements. Basically this means that there would have to be a bug in the std
Scala library which would seem highly unlikely. I knew I was counting double
because all my results where even numbers. After thinking about it for a while
I decided to investigate the graph file, it turns out that every connection
is made double, so the double counting was in fact correct.

\section{TODO}
MLS with several results
GLS -> I think the localsearch will recursively unecesrly decend into its members
because the local search is packed in the member factory. Maybe remove the
local search from the memberfactory?

\section{Results}
\subsection{Time}
\pgfplotstableread{runtimes.table}\dataTable
\begin{tikzpicture}
\pgfplotsset{set layers}
\begin{axis}[
	ybar stacked,
	xlabel={Algorithm},
	xticklabels from table={runtimes.table}{name},
	xtick=data,
	x tick label style={rotate=90,anchor=east},
	ylabel={Time}
]

@@

\input{runtimes.textable}

\subsection{Optima}
\pgfplotstableread{results.table}\dataTable
\begin{tikzpicture}
\pgfplotsset{set layers}
\begin{axis}[
	ybar stacked,
	xlabel={Algorithm},
	xticklabels from table={results.table}{name},
	xtick=data,
	x tick label style={rotate=90,anchor=east},
	ylabel={Fitness (less is better)}
]
% Layers needed to get error bars on top of lower blue rectangle
\addplot[color=white]
table[on layer=axis grid, x expr=\coordindex, y=firsty]{\dataTable};

\end{tikzpicture}
\\
\input{results.textable}
\end{empfile}
\end{document}
